%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Guide- Dr. Tavpreet Sethi, IIITD} % Organisation
    {\href{https://github.com/Abdul-Aziz-Mustafa/Discovery-Potion}{GitHub Discovery Potion}} % Project
    {New Delhi, India} % Location
    {Jan 2022 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {We created an ML model that finds the best drug amongst a
number of drugs to cure Alzheimer's. We used different features
such as IC50 values, canonical smiles notation, pIC50 values for
the drug for detailed analysis. We further made a web
application.}
        % \item {}
        % \item {}
        \item {\textbf{Technical Skills:} Streamlight, python (SciKit Learn, Pandas, Pickle, Numpy, python Notebook, ML.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Presentation skills.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Guide:- C. Anantaram, IIITD} % Organisation
    {\href{https://github.com/Abdul-Aziz-Mustafa/RAAH}{RAAH CAB-BOOKING WEB APP}} % Project
    {New Delhi, India} % Location
    {Jan 2022 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a simple cab booking app with a database designed in MYSQL and web app in vanillaJs framework}
        \item {\textbf{Technical Skills:} Javascript, Ejs, Express js, MYSQL,HTML,CSS,Node JS, PL-SQL.}
        \item {\textbf{Soft Skills:} Time Management, Presentation skills, Teamwork, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Guide- Sujay Deb, IIITD} % Organisation
    {\href{https://github.com/shaknoah/ASSEMBLER-AND-SIMULATOR}{Assembler and Simulator}} % Project
    {New Delhi, India} % Location
    {Aug2021 - October 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Design and implemented A custom assembler and custom
Simulator for a given ISA.}
        \item {\textbf{Technical Skills:} Python.}
        \item {\textbf{Soft Skills:}Leadership, Time Management, Teamwork, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
